### 2024-02-28 texts/paper_closing.tex
integrate popcircles (for now million in 10km circle),
as part of that, include in gc_vvs, adjust gt_sumstats (decimal digits generation account for non-Int min/max), improve gd_pmyear (now gw_pmyear) to just merge, yeeting rows now moved to (new) gd_pmyear function, cleanup old code

% Created 2024-01-11 do 13:48
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

\setlength{\parindent}{1.2cm}
\author{Johannes }
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Johannes },
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 29.1 (Org mode 9.6.7)}, 
 pdflang={English}}
\begin{document}

@@

@@

% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Fri Dec  8 22:31:01 2023
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & 276 & 0.575 &  0.592 &  0.49 & 0 &  1 \\ 
   & Gender - Female & 76 & 0.158 &  0.168 &  0.37 & 0 &  1 \\ 
   & Gender - Couple & 128 & 0.267 &  0.240 &  0.43 & 0 &  1 \\ 
   & Founder died & 58 & 0.121 &  0.093 &  0.29 & 0 &  1 \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & 179 & 0.373 &  0.408 &  0.49 & 0 &  1 \\ 
   & Self-Identification - Foundation & 101 & 0.210 &  0.191 &  0.39 & 0 &  1 \\ 
   & Self-Identification - Collection & 74 & 0.154 &  0.141 &  0.35 & 0 &  1 \\ 
   & Self-Identification - Other & 126 & 0.263 &  0.261 &  0.44 & 0 &  1 \\ 
   & Founder name in Museum name & 229 & 0.477 &  0.487 &  0.50 & 0 &  1 \\ 
   & MOW inclusion & 91 & 0.190 &  0.296 &  0.46 & 0 &  1 \\ 
   & AN Ranking - Not Included &  &  &  0.794 &  0.40 & 0 &  1 \\ 
   & AN Ranking - Included &  &  &  0.149 &  0.36 & 0 &  1 \\ 
   & AN Ranking - Dropped &  &  &  0.057 &  0.23 & 0 &  1 \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density &  &  & 20.541 & 18.37 & 1 & 62 \\ 
   & Europe and North America & 313 & 0.652 &  0.645 &  0.48 & 0 &  1 \\ 
   & Region - Africa & 7 & 0.015 &  0.012 &  0.11 & 0 &  1 \\ 
   & Region - Asia & 128 & 0.267 &  0.281 &  0.45 & 0 &  1 \\ 
   & Region - Europe & 242 & 0.504 &  0.502 &  0.50 & 0 &  1 \\ 
   & Region - Latin America & 22 & 0.046 &  0.042 &  0.20 & 0 &  1 \\ 
   & Region - North America & 71 & 0.148 &  0.144 &  0.35 & 0 &  1 \\ 
   & Region - Oceania & 10 & 0.021 &  0.019 &  0.14 & 0 &  1 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Fri Dec  8 22:38:34 2023
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_more}\\ 
 \hline
  \multicolumn{3}{l}{\textbf{Founder}} \\ 
 & Gender - Female & .30 \; (0.36) \\ 
   & Gender - Couple & -.03 \; (0.36) \\ 
   & Founder died & .04 \; (0.54) \\ 
   \multicolumn{3}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .79 \; (0.47) \\ 
   & Self-Identification - Collection & .50 \; (0.55) \\ 
   & Self-Identification - Other & 1.18 \; (0.37)^{**} \\ 
   & AN Ranking - Included & .34 \; (0.41) \\ 
   & AN Ranking - Dropped & 1.16 \; (0.45)^{*} \\ 
   & Founder name in Museum name & -.35 \; (0.32) \\ 
   & MOW inclusion & -.88 \; (0.39)^{*} \\ 
   \multicolumn{3}{l}{\textbf{Environment}} \\ 
 & PM density & -.04 \; (0.03) \\ 
   & PM density$^{2}$ & .00 \; (0.00) \\ 
   \hline
 & Museum-years & 6903 \\ 
   & Closures & 53 \\ 
   & log. Likelihood & -266.76 \\ 
   & AIC & 557.52 \\ 
   & BIC & 581.16 \\ 
   \hline 
 \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}

>>>>

% Created 2024-02-28 wo 13:52
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

\setlength{\parindent}{1.2cm}
\author{Johannes }
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Johannes },
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 29.2 (Org mode 9.6.15)}, 
 pdflang={English}}
\begin{document}

@@

\bigbreak
\noindent
\textbf{keywords}: museum, closure, identity

@@

% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Wed Feb 28 13:49:39 2024
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & 276 & 0.575 &  0.592 &  0.49 & 0 & 1 \\ 
   & Gender - Female & 76 & 0.158 &  0.168 &  0.37 & 0 & 1 \\ 
   & Gender - Couple & 128 & 0.267 &  0.240 &  0.43 & 0 & 1 \\ 
   & Founder died & 58 & 0.121 &  0.093 &  0.29 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & 179 & 0.373 &  0.408 &  0.49 & 0 & 1 \\ 
   & Self-Identification - Foundation & 101 & 0.210 &  0.191 &  0.39 & 0 & 1 \\ 
   & Self-Identification - Collection & 74 & 0.154 &  0.141 &  0.35 & 0 & 1 \\ 
   & Self-Identification - Other & 126 & 0.263 &  0.261 &  0.44 & 0 & 1 \\ 
   & Founder name in Museum name & 229 & 0.477 &  0.487 &  0.50 & 0 & 1 \\ 
   & MOW inclusion & 91 & 0.190 &  0.296 &  0.46 & 0 & 1 \\ 
   & AN Ranking - Not Included &  &  &  0.794 &  0.40 & 0 & 1 \\ 
   & AN Ranking - Included &  &  &  0.149 &  0.36 & 0 & 1 \\ 
   & AN Ranking - Dropped &  &  &  0.057 &  0.23 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density &  &  & 20.541 & 18.37 & 1 & 62 \\ 
   & Population (10km Circle) &  &  &  1.401 &  1.76 & 0.000091 & 10.95 \\ 
   & Europe and North America & 313 & 0.652 &  0.645 &  0.48 & 0 & 1 \\ 
   & Region - Africa & 7 & 0.015 &  0.012 &  0.11 & 0 & 1 \\ 
   & Region - Asia & 128 & 0.267 &  0.281 &  0.45 & 0 & 1 \\ 
   & Region - Europe & 242 & 0.504 &  0.502 &  0.50 & 0 & 1 \\ 
   & Region - Latin America & 22 & 0.046 &  0.042 &  0.20 & 0 & 1 \\ 
   & Region - North America & 71 & 0.148 &  0.144 &  0.35 & 0 & 1 \\ 
   & Region - Oceania & 10 & 0.021 &  0.019 &  0.14 & 0 & 1 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Wed Feb 28 13:49:45 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_more}\\ 
 \hline
  \multicolumn{3}{l}{\textbf{Founder}} \\ 
 & Gender - Female & .24 \; (0.36) \\ 
   & Gender - Couple & .02 \; (0.36) \\ 
   & Founder died & .05 \; (0.53) \\ 
   \multicolumn{3}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .90 \; (0.47) \\ 
   & Self-Identification - Collection & .64 \; (0.56) \\ 
   & Self-Identification - Other & 1.28 \; (0.37)^{***} \\ 
   & AN Ranking - Included & .28 \; (0.41) \\ 
   & AN Ranking - Dropped & 1.15 \; (0.45)^{*} \\ 
   & Founder name in Museum name & -.36 \; (0.32) \\ 
   & MOW inclusion & -.86 \; (0.40)^{*} \\ 
   \multicolumn{3}{l}{\textbf{Environment}} \\ 
 & PM density & -.04 \; (0.03) \\ 
   & PM density$^{2}$ & .00 \; (0.00) \\ 
   & Population (10km Circle) & .14 \; (0.07) \\ 
   \hline
 & Museum-years & 6903 \\ 
   & Closures & 53 \\ 
   & log. Likelihood & -265.13 \\ 
   & AIC & 556.26 \\ 
   & BIC & 581.87 \\ 
   \hline 
 \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}
